Exposure Consequences - Statistics and Figures

### 2018-05-10 ManuscriptMaterials.Rmd
Switched to Satterthwaite estimates for all LME analyses.

---
title: "Exposure Consequences - Statistics and Figures"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
---

@@

@@

```{r RAE_exposure,include=TRUE}
exposureNoCursorChange()
```

@@

```{r RAE_exp_iterations}
exposureAftereffectsPersistent()
```

@@

```{r RAE_exp_cla}
exposureClassicReachAftereffects()
```

@@

```{r loc_exp}
exposureLocalization(remove15=TRUE)
```

@@

```{r loc_exp_movtype}
exposureLocalizationShift(remove15=TRUE)
```

@@

```{r loc_ombnibus}
groupLocalization(model='full',remove15=TRUE)
```

@@

```{r loc_groups_movementtype}
groupLocalization(model='movementtype',remove15=TRUE)
```

@@

```{r loc_cla}
classicLocalizationShift(remove15=TRUE)
```

>>>>

---
title: "Exposure Consequences - Statistics and Figures"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
---

@@

## Analyses

Since in the localization tasks there is missing data at some points (usually at the extremes) we can't use ANOVAs directly on the data. Imputation is going to be very hard because the missing data is systematically missing. Hence, we are using Linear Mixed Effects models as an alternative, but this presents a new problem. Getting the usual F-values and p-values is not so straightforward. Initially we decided to use the $\chi^2$ approach that we get from the `Anova` function from the `car` package. However, a paper from Steven G. Luke (2017, _Evaluating significance in linear mixed-effects models in R_) suggests using Sattertwaite approximation. So all functions running an LME now take an argument that tells them to use the Satterthwaite method, but the default is chi-squared. It turns out that it doesn't matter much, so it's a good sanity check. For consistency across all the analyses, we set the value of that argument is set here:

```{r}
LMEmethod <- 'Satterthwaite'
# options: Satterthwaite, chi-squared
```

@@

```{r RAE_exposure,include=TRUE}
exposureNoCursorChange(LMEmethod=LMEmethod)
```

@@

```{r RAE_exp_iterations}
exposureAftereffectsPersistent(LMEmethod=LMEmethod)
```

@@

```{r RAE_exp_cla}
exposureClassicReachAftereffects(LMEmethod=LMEmethod)
```

@@

```{r loc_exp}
exposureLocalization(remove15=TRUE, LMEmethod=LMEmethod)
```

@@

```{r loc_exp_movtype}
exposureLocalizationShift(remove15=TRUE, LMEmethod=LMEmethod)
```

@@

```{r loc_ombnibus}
groupLocalization(model='full', remove15=TRUE, LMEmethod=LMEmethod)
```

@@

```{r loc_groups_movementtype}
groupLocalization(model='movementtype', remove15=TRUE, LMEmethod=LMEmethod)
```

@@

```{r loc_cla}
classicLocalizationShift(remove15=TRUE, LMEmethod=LMEmethod)
```
